\huge Microbial Interaction Database pipeline - Figures draft \#2

### 2019-03-25 figures.tex
Update supplementary figures
Update: Figure 1
Add figure 6

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure1.pdf}
  \caption{
    \textbf{The workflow of the microbial co-occurrence analysis pipeline}.
    The processes can be grouped into four major steps: \textbf{(A)} denoising and clustering, \textbf{(B)} taxonomy assignment, \textbf{(C)} OTU/ESV processing, and \textbf{(D)} network inference.
    Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
    \textbf{(E)} shows the average variances in the final networks contributed by each of the four groups over all the test datasets
  }
  \label{fig:main_figure}
\end{figure}

@@

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/all_denoise_reg.pdf}
  \caption{All pairwise correlations comparing the similarity between different denoising and clustering methods}
  \label{fig:figures2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/denoise_network.pdf}
  \caption{A network showing union and intersection of networks generated using certain combination of methods}
  \label{fig:pdf/denoise_network}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{figure1.pdf}
  \caption{
    \textbf{The workflow of the microbial co-occurrence analysis pipeline}.
    The processes can be grouped into four major steps: \textbf{(A)} denoising and clustering, \textbf{(B)} taxonomy assignment, \textbf{(C)} OTU/ESV processing, and \textbf{(D)} network inference.
    Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
    \textbf{(E)} shows the average variances in the final networks contributed by each of the four groups over all the test datasets
  }
  \label{fig:main_figure}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{figure6.pdf}
  \caption{
    \textbf{The choice of database contributes to the most variance in the networks}.
    \textbf{(A)} The relative variance in the networks contributed by the denoising, taxonomy assignment and filtering steps.
    \textbf{(B)} The PCA plot clearly shows that the networks can be separated based on database
  }
  \label{fig:figure1}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/all_denoise_reg.pdf}
  \caption{All pairwise correlations comparing the similarity between different denoising and clustering methods}
  \label{fig:figures3}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{png/hamming_distance.png}
  \caption{The hamming distance between the networks is shown. The similarity between various methods was found to vary with the data-source used.}
  \label{fig:figures4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pdf/denoise_network.pdf}
  \caption{A network showing union and intersection of networks generated using certain combination of methods}
  \label{fig:figures5}
\end{figure}
